Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-27 latex/comp_or.tex
paper CompOR updtate

In line \ref{tour:minRampDist}, $minRampDist$ minimizes the distance of the next node destined pallets, keeping the CG in its operational range. This procedure is implemented in integer programming as presented in Subsection \ref{improvement}, according to equations \ref{eq:distobj} to \ref{eq:disttorque}.

$ScoreAndDeviation$ evaluates the allocation graph generated by $SolveNode$, returning the corresponding score and CG deviation. It consists of a loop that goes through all the pallets, accumulating the scores and the torques of the shipped items, allowing the final calculation of the CG deviation.

@@

@@

Finally, we present a new heuristic designed specifically for ACLP+RPDP, which we named \emph{mpShims}. Like in mechanics, shims are collections of spacers to fill gaps, which may be composed of parts with different thicknesses (see Figure \ref{fig:shims}). This strategy is based on a practical observation: usually, subsets of smaller and lighter items are saved for later adjustments to the remaining clearances.

@@

		\begin{tikzpicture}[scale=0.75, samples=100]
			\filldraw[fill=blue!3!white, draw=black] (0, 0) rectangle (12.5, 5.5);
			\draw[->] (.2, .6) -- coordinate (x axis mid) (12, .6);
			\node at (5, 0.3) {$\eta_1[i]$};
			\node at (5, 2.5) {|};
			\node at (6, 2.5) {shims};
			\node at (7, 2.5) {|};
			\node at (7, 0.3) {$\eta_2[i]$};
			\node at (0.3, 5) {$\theta_{ij}^{\pi_k}$};
			\draw[->] (.6, .2) -- coordinate (y axis mid) (0.6, 5.3);
			\node at (12, 0.3) {$e_{ij}^{\pi_k}$};
			\draw[smooth, domain = 0.09:2, color=black, thick] plot (.3+1/\x,{4.2+log2(\x)});
			\draw[->, dashed] (5, 0.6)--(5, 2.0);
			\draw[->, dashed] (7, 0.6)--(7, 1.5);
		\end{tikzpicture}

@@

Figure \ref{fig:whip} represents the $n^{\pi_k}$\/ possible edges $e_{ij}^{\pi_k}$\/ of $p_i$\/ sorted by $\theta_{ij}^{\pi_k}$. \emph{mpShims}\/ starts with a greedy solution for each pallet, stopping at the edge with index in $\eta_1^i$ close to the local optimum (first phase). Then, performs an integer programming procedure to minimize the CG deviation (second phase), and finally, considering even the edge with the index $\eta_2^i$, it elaborates different possible complements for this pallet and selects the best of these complements (third phase).

Although the third phase solves a {\it Knapsack Problem}, a faster algorithm for solving a {\it Bin Packing Problem} was used ({\it the First Fit Decreasing - FFD}), and the most profitable bin ({\it Shims}) was selected. This method was proved to be faster than a {\it Dynamic Programming} solution for the {\it Knapsack Problem}.

	In this work, we included a new phase after the first: a minimization of the CG deviation. An integer programming procedure that helps improve the overall {\it mpShims} results.

@@

$3^{st}$ - {\it Shims} set construction and best {\it Shims} selection
ess run-time, we considered each pallet as a parallel process, taking advantage of nowadays multi-core computers.

@@

		\State $ts \gets 2.0$ \Comment{torque surplus} \label{mpShims:ts}

@@

Line \ref{mpShims:ts} defines the torque surplus ($ts$). For the greedy phase, the solution may generate torque infeasible solutions with doubled torque ($2.0$), which will be repaired by the next phase, the minimization of the CG deviation.

@@

Line \ref{mpShims:minCGdev} calls the $minCGdev$ integer programming method (Subsection \ref{subsection:second_phase}) which updates the $nodeTorque$ and $G$. $minCGdev$ minimizes the CG deviation. We raise the hypothesis that, in sequential mode, where one pallet is built at a time, torque constraints may be more restrictive than volume or weight constraints, which could stop the palletization process earlier, fostering a solution that may be not as good as it could be. So, we decided to balance cargo before the next {\it Shims} phase to allow more room for pallet fulfillment. This will be confirmed (or not) in Section \ref{sec6}.

Line \ref{mpShims:getBestShims} calls the $getBestShims$ method which updates $p_i$, $N^{\pi_k}$, $nodeTorque$, and $G$.

Line \ref{mpShims:join2} wait for all $getBestShims$ processes to finish.

@@

\subsubsection{{\it mpShims} first phase}

@@

			\State $E_N^{\pi_k} \gets E_N^{\pi_k} \cup \{e_{ij}^{\pi_k}\}$ 
			\State $volume_i \gets volume_i + t_j^{\pi_k}.v$
			\State $\eta_1^i \gets \eta_1^i + 1$ 
			\State $\tau^{\pi_k} \gets \tau^{\pi_k} + \Delta\tau$

@@

Line \ref{greedy:ts} presents the variable $ts$ (torque $\tau$ surplus), that is an extra-torque limit to allow each greedy pallet construction to, temporally, exceed the torque limit, that will be turned feasible again by the next {\it mpShims}' phase, the CG minimization phase. $ts$ value will be adjusted empirically, by means of the {\it iRace} tool (\cite{LopezIbanezManuel2016}), to produce feasible solutions in all problem instances.

\subsubsection{{\it mpShims} second phase}
\label{subsection:second_phase}

@@

Equation \ref{eq:distobjshims} minimizes the aircraft absolute torque in node $\pi_k$, where 140 is the weight of an empty pallet, $a^{\pi_k}_q.w$ the weight of the consolidated, and $p_i.D$ the distance between the pallet centroid to the aircraft CG; Equation \ref{eq:distconsshims} states that each consolidated will be assigned to exactly one pallet; and Equation \ref{eq:distpalletsshims} states that each pallet will receive one consolidated.

\subsubsection{{\it mpShims} third phase}

@@

		\For{$x \gets \eta_1^i$ to $\eta_2^i$} \label{edges_indexes}

		\State $NewShims \gets$ {\bf True} \label{new_shims}
		\State $e_{ij}^{\pi_k} \gets E_x^i$

@@

From a list of items, items are sorted from the biggest to the smallest and placed in such an order on a pallet.Each item has 1 to 6 orientations to choose from when it can be placed. The orientation procedure can select the best direction type among possible orientations.

A pivot point is used to determine item's position. The pivot is an (x, y, z) coordinate which represents a point in the pallet at which an attempt to pack an item will be made.

The back lower left corner of the item will be placed at the pivot. If the item cannot be packed at the pivot position then it is rotated until it can be packed at the pivot point or until we have tried all 6 possible rotation types.

If, after rotating it, the item still cannot be packed at the pivot point, then we move on to packing another item and add the unpacked item to a list of items that will be packed after an attempt to pack the remaining items is made.

The first pivot in the empty pallet is always (0,0,0). When one item can be placed into multiple optimal pivot point, the placement selection module can help make a choice.

Let $n$ be the number of items and $m$ the number of pallets.

Let $A_{j}\ =\ 1$ if item $j$ is assigned to the pallet, $A_{j}\ =\ 0$ otherwise, for $j \in \{1,\ 2,\ 3,\ ...,\ n\}$.

Let $X_{ij}\ =\ 1$ if item $j$ was already assigned to pallet $i$ by {\it mpShims}, $X_{ij}\ =\ 0$ otherwise, for $i \in \{1,\ 2,\ 3,\ ...,\ m\}$.

Let $d_j,\ w_j,\ h_j$ be parameters indicating the depth, width, and height of an item. 
Let $D_i,\ W_i,\ H_i$ be parameters indicating the depth, width, and height of the pallet.

@@

Let $o_j^1,\ o_j^2,\ o_j^3,\ o_j^4,\ o_j^5,\ o_j^6$ be binary variables, indicating the possible orientations for item $j$. One of the values equal to 1 if item $j$ has orientation in $\{1,\ 2,\ 3,\ 4,\ 5,\ 6\}$, respectively, otherwise equal to 0.

\begin{equation} \label{eq:3dpacking1}
	\mbox{minimize} \Big [ D_i \times W_i \times H_i - \sum_{j \gets 1}^{n} X_{ij} \times A_{j} \times d_j \times w_j \times h_j \Big ]
\end{equation}

\begin{equation} \label{eq:3dpacking2}
	\sum_{j \gets 1}^{n} A_{j} \times d_j  \leq X_{ij} \times D_i,\ i \in \{1,\ 2,\ 3,\ ...,\ m\}
\end{equation}

\begin{equation} \label{eq:3dpacking3}
	\sum_{j \gets 1}^{n} A_{j} \times w_j  \leq X_{ij} \times W_i,\ i \in \{1,\ 2,\ 3,\ ...,\ m\}
\end{equation}

\begin{equation} \label{eq:3dpacking4}
	\sum_{j \gets 1}^{n} A_{j} \times h_j  \leq X_{ij} \times H_i,\ i \in \{1,\ 2,\ 3,\ ...,\ m\}
\end{equation}

@@

In line \ref{3dpacking:3}, $N^{\pi_k}_i$ is the set of items previously assigned to pallet $i$.

@@

\begin{equation} \label{eq:distpalletw}
	p_i.W = 140 + a^{\pi_k}_q.w ;\ i \in \{1,2,\ldots,m\};\ q \in \{1,2,\ldots,m\}
\end{equation}

\begin{equation} \label{eq:disttorque}
	s.t.:\ | \sum\ p_i.D * p_i.W\ | \leq maxW \times limit^{CG}_{long} ;\ i \in \{1,2,\ldots,m\}
\end{equation}

Equation \ref{eq:distobj} minimizes the sum of distances of the consolidated in node $\pi_k$ destined to the next node $\pi(k+1)$; Equation \ref{eq:distcons} states that each consolidated will be assigned to exactly one pallet; Equation \ref{eq:distpallets} states that each pallet will receive one consolidated; Equation \ref{eq:distpalletw} calculates the total weight of each pallet; and Equation \ref{eq:disttorque} guarantees that the torque limit will not be exceeded.

@@

A relevant problem with meta-heuristics is the parameter's adjustment to extract the best possible efficiency in the optimization. The bulk of the tools to fine-tune these parameters utilize a statistical backdrop that enables them to make accurate predictions regarding the differences in candidate configurations' performance. Inadequacies in the design of the statistical experiment may therefore lead to erroneous results from the statistical tests and, subsequently, cause the approach to produce inaccurate comparisons of candidate configurations. That is why all parameters were set using the $iRace$ package \cite{LopezIbanezManuel2016}. Supplying $iRace$ with a range for $volThreshold$ as [0.80 to 0.99], {\it iRace} yielded 0.92, by training on the uneven instances numbers. The values tested for 20\%, 50\%, and 100\% volume surpluses were very close, considering the confidence level offered by {\it iRace}.

For parallelization, we used the {\it Python Multiprocessing} package, which implements {\it process-based parallelism} or {\it parallel shared memory algorithm}. According to \cite{multiprocessing}, {\it Multiprocessing} is a package that supports spawning processes using an API similar to the {\it Python Threading} package.

According to \cite[p.271]{Breshears2009}, a {\it Process} is the operating system’s spawned and controlled entity that encapsulates an executing application. A process has two main jobs: the first is to hold the application's resources, and the second is to carry out the application's instructions.

@@

@@

\vspace{2.0mm}
\begin{table}[!ht]
\centering
\caption{Average distances minimization}  \label{tab:ground}
%\footnotesize
\scriptsize
\begin{tabular}{c S[table-format=-1.1] S[table-format=-1.1] S[table-format=-1.3]}
\toprule
& {\bf Before} & {\bf After} & {\bf Improvement} \\
{\bf Scenario} & {\bf (m)}    & {\bf (m)}   & {\bf (\%)} \\		
\midrule
$1$ &  32.7 & 28.7 & -12.3 \\ % CBC 32.1 & 31.3 & -2.4 Shims 34.0 & 29.5 & -13.1, 31.5 & 29.9 & -5.1
$2$ & 193.3 & 188.9 & -2.3 \\ % mpShims 212.0 & 188.9 & -10.9
$3$ & 165.1 & 153.3 & -7.1 \\ % 
$4$ & 134.0 & 130.7 & -2.4 \\ % CBC 137.1 & 132.0 & -3.7 mpShim 143.4 & 136.6 & -4.7
$5$ & 118.0 & 116.1 & -1.6 \\ % CBC 124.9 & 116.3 & -6.9 mpShim 126.7 & 122.0 & -3.8 
$6$ & 105.2 & 104.8 & -0.4 \\ % CBC 117.4 & 107.6 & -8.3 mpShim 115.3 & 110.4 & -4.2                                                                
\bottomrule
\end{tabular}
\end{table}

Table \ref{tab:ground} presents the distances minimization of the next node destined pallets to the ramp door. Columns {\bf Before} and {\bf After} refer to the application of the current method.

@@

(4) The distances to move pallets on unloading in the next node could be minimized to benefit ground handling costs.
This hypothesis was confirmed by the results on Table \ref{tab:ground}, although in Scenario 3 this procedure could not improve in any of the volume surplus instances (1.2, 1.5, and 2.0).

A new question is raised about whether it is worth using parallelism as, although {\it mpShims} was twice as fast as {\it Shims}, the results of {\it Shims} were still better than those of {\it mpShims}. May this question be solved through the real-world application of these methods.

@@

Other important contributions are that we checked four hypotheses: Computer parallelism improved {\it Shims} performance; the intermediate integer programming procedure added to {\it Shims} algorithm enhanced it's results; but the integer programming procedure to minimize pallets' travel in the cargo bay did not improve the results; and a procedure for 3-D packing was turned possible for operational use due to a process-based parallel computing heuristic.

>>>>

{\color{purple}
In line \ref{tour:3dpacking}, $3Dpacking(G)$ packs the items previously assigned to a pallet, which is feasible in terms of volume, weight, and torque but still not guaranteed to fit into the pallet. In this procedure, some unfit items are excluded from the solution.
}

{\color{blue}
In line \ref{tour:minRampDist}, $minRampDist(G)$ minimizes the distance of the next node destined pallets, keeping the CG in its operational range. This procedure is implemented in integer programming. This method does not affect palletization or the objective function value.
}

$ScoreAndDeviation(\pi(k), G_4)$ evaluates the allocation graph generated by $SolveNode$, returning the corresponding score and CG deviation. It consists of a loop that goes through all the pallets, accumulating the scores and the torques of the shipped items, allowing the final calculation of the CG deviation.

@@

In this work, we had to select the {\it fully-connected} topology because the list of items to embark and the aircraft torque must be accessible for reading and writing by all child processes.

@@

Finally, we present a new multiprocessing heuristic designed specifically for ACLP+RPDP, which we named \emph{mpShims}. Like in mechanics, shims are collections of spacers to fill gaps, which may be composed of parts with different thicknesses (see Figure \ref{fig:shims}). This strategy is based on a practical observation: usually, subsets of smaller and lighter items are saved for later adjustments to the remaining clearances.

@@

		\begin{tikzpicture}[scale=0.75, samples=100]
			\filldraw[fill=blue!3!white, draw=black] (0, 0) rectangle (12.5, 5.5);
			\draw[->] (.2, .6) -- coordinate (x axis mid) (12, .6);
			\node at (5, 0.3) {$\eta_1^{\ i}$};
			\node at (5, 2.5) {|};
			\node at (6, 2.5) {shims};
			\node at (7, 2.5) {|};
			\node at (7, 0.3) {$\eta_2^{\ i}$};
			\node at (0.3, 5) {$\theta_{ij}^{\pi_k}$};
			\draw[->] (.6, .2) -- coordinate (y axis mid) (0.6, 5.3);
			\node at (12, 0.3) {$e_{ij}^{\pi_k}$};
			\draw[smooth, domain = 0.09:2, color=black, thick] plot (.3+1/\x,{4.2+log2(\x)});
			\draw[->, dashed] (5, 0.6)--(5, 2.0);
			\draw[->, dashed] (7, 0.6)--(7, 1.5);
		\end{tikzpicture}

@@

Figure \ref{fig:whip} represents the $n^{\pi_k}$\/ possible edges $e_{ij}^{\pi_k}$\/ of $p_i$\/ sorted by $\theta_{ij}^{\pi_k}$. \emph{mpShims}\/ starts with a greedy solution for each pallet, stopping at the edge with index in $\eta_1^{\ i}$ close to the local optimum (first phase). Then, performs an integer programming procedure to minimize the CG deviation (second phase), and finally, considering even the edge with the index $\eta_2^{\ i}$, it elaborates different possible complements for this pallet and selects the best of these complements (third phase).

Although the third phase solves a {\it Knapsack Problem}, a faster algorithm for solving a {\it Bin Packing Problem} was used ({\it the First Fit Decreasing - FFD}), and the most profitable bin ({\it Shims}) was selected.

@@

$3^{st}$ - {\it Shims} set construction and best {\it Shims} selection.

In the first and third phases, we considered each pallet as a parallel process, taking advantage of nowadays multi-core computers.

@@

		\State $ts \gets 1.2$ \Comment{torque surplus} \label{mpShims:ts}

@@

Line \ref{mpShims:ts} defines the torque surplus ($ts$). For the $Greedy$ phase, the solution may generate temporary torque unfeasible solutions. We raised the Hypothesis (2) that, in sequential mode, where one pallet is built at a time, torque constraints may be more restrictive than volume or weight constraints, which could stop the palletization process earlier, fostering a solution that may be not as good as it could be. So, we decided to extend torque limit and balance cargo before the next {\it Shims} phase to allow more room for pallet fulfillment.

@@

Line \ref{mpShims:minCGdev} calls the $minCGdev()$ integer programming method (Subsection \ref{subsection:second_phase}) which updates the $nodeTorque$ and $G$. $minCGdev()$ minimizes the CG deviation, bringing it back to its operational range. A proper value for $ts$ must be empirically found to guarantee this intent (the {\it iRace} tool (\cite{LopezIbanezManuel2016}) is good for this value determination).

Line \ref{mpShims:getBestShims} calls the $getBestShims()$ method which updates $p_i$, $N^{\pi_k}$, $nodeTorque$, and $G$.

Line \ref{mpShims:join2} wait for all $getBestShims()$ processes to finish.

@@

\subsubsection{The {\it mpShims} first phase}

@@

			\State $E_N^{\pi_k} \gets E_N^{\pi_k} \cup \{e_{ij}^{\pi_k}\}$ 
			\State $volume_i \gets volume_i + t_j^{\pi_k}.v$
			\State $\eta_1^{\ i} \gets \eta_1^{\ i} + 1$ 
			\State $\tau^{\pi_k} \gets \tau^{\pi_k} + \Delta\tau$

@@

Line \ref{greedy:ts} presents the variable $ts$ (torque surplus), that is an extra-torque limit to allow each greedy pallet construction to, temporally, exceed the torque limit, that will be turned feasible again by the next {\it mpShims}' phase, the CG minimization phase.

\subsubsection{The {\it mpShims} second phase}
\label{subsection:second_phase}

@@

Equation \ref{eq:distobjshims} minimizes the aircraft absolute torque in node $\pi_k$, where 140kg is the weight of an empty pallet, $a^{\pi_k}_q.w$ the weight of the consolidated, and $p_i.D$ the distance between the pallet centroid to the aircraft CG; Equation \ref{eq:distconsshims} states that each consolidated will be assigned to exactly one pallet; and Equation \ref{eq:distpalletsshims} states that each pallet will receive one consolidated.

\subsubsection{The {\it mpShims} third phase}

@@

		\For{$x \gets \eta_1^{\ i}$ to $\eta_2^{\ i}$} \label{edges_indexes}

		\State $NewShims \gets$ {\bf True} \label{new_shims}
		\State $e_{ij}^{\pi_k} \gets E_x^{\ i}$

@@

\begin{itemize}
	\item[1] From a list of items assigned to a pallet, items are sorted from the biggest to the smallest and placed in such an order on a pallet. Each item has 1 to 6 orientations to choose from when it can be placed. The orientation procedure can select the best direction type among possible orientations.
	\item[2] A pivot point is used to determine item's position. The pivot is an (x, y, z) coordinate which represents a point in the pallet at which an attempt to pack an item will be made.
	\item[3] The back lower left corner of the item will be placed at the pivot. If the item cannot be packed at the pivot position then it is rotated until it can be packed at the pivot point or until we have tried all 6 possible rotation types.
	\item[4] If, after rotating it, the item still cannot be packed at the pivot point, then we move on to packing another item and add the unpacked item to a list of items that will be packed after an attempt to pack the remaining items is made.
	\item[5] The first pivot in the empty pallet is always (0, 0, 0). When one item can be placed into multiple optimal pivot point, the placement selection module can help make a choice.
\end{itemize}

Let $n^i$ be the number of items assigned to pallet $i$ and $m$ the number of pallets.

Let $A_{j} = 1$ if item $t_j$ is assigned to the pallet, $A_{j}\ =\ 0$ otherwise, for $j \in \{1,\ 2,\ 3,\ ...,\ n^i\}$.

Let $X_{ij} = 1$ if item $j$ was already assigned to pallet $i$ by {\it mpShims}, $X_{ij}\ =\ 0$ otherwise.

Let $t_j.d,\ t_j.wh,\ t_j.h$ be parameters indicating the depth, width, and height of an item.

Let $p_i.Dh,\ p_i.Wh,\ p_i.H$ be parameters indicating the depth, width, and height of the pallet. We included letter $h$ at the end of parameters $p_i.Dh$ and $p_i.Wh$ to turn them different from $p_i.D$ (distance from CG) and $p_i.W$ (weight limit).

@@

Let $t_j.o^1,\ t_j.o^2,\ t_j.o^3,\ t_j.o^4,\ t_j.o^5,\ t_j.o^6$ be binary variables, indicating the possible orientations for item $t_j$.

\begin{equation} \label{eq:3dpacking1}
	\mbox{minimize} \Big [ p_i.Dh \times p_i.Wh \times p_i.H - \sum_{j \gets 1}^{n^{\ i}} X_{ij} \times A_{j} \times t_j.d \times t_j.wth \times t_j.h \Big ]
\end{equation}

\begin{equation} \label{eq:3dpacking2}
	\sum_{j \gets 1}^{n^{\ i}} A_{j} \times t_j.d  \leq X_{ij} \times p_i.D\ i \in \{1,\ 2,\ 3,\ ...,\ m\}
\end{equation}

\begin{equation} \label{eq:3dpacking3}
	\sum_{j \gets 1}^{n^{\ i}} A_{j} \times t_j.wh  \leq X_{ij} \times p_i.Wh,\ i \in \{1,\ 2,\ 3,\ ...,\ m\}
\end{equation}

\begin{equation} \label{eq:3dpacking4}
	\sum_{j \gets 1}^{n^{\ i}} A_{j} \times t_j.h  \leq X_{ij} \times p_i.H,\ i \in \{1,\ 2,\ 3,\ ...,\ m\}
\end{equation}

\begin{equation} \label{eq:3dpacking5}
t_j.o^1 + t_j.o^2 + t_j.o^3 + t_j.o^4 + t_j.o^5 + t_j.o^6 = 1
\end{equation}

Equation \ref{eq:3dpacking1} minimizes the volume slack; equations \ref{eq:3dpacking2}, \ref{eq:3dpacking3}, and \ref{eq:3dpacking4} constrains the packing to the three dimensions; and \ref{eq:3dpacking5} guarantees that only one orientation is chosen for the item.

@@

In line \ref{3dpacking:3}, $N^{\pi_k}_i$ is the set of items previously assigned to pallet $i$ and the method $3Dpacker()$ conforms to equations \ref{eq:3dpacking1}, \ref{eq:3dpacking2}, \ref{eq:3dpacking3}, \ref{eq:3dpacking4}, and \ref{eq:3dpacking5}.

@@

\begin{equation} \label{eq:distpalletw}
	p_i.w = 140 + a^{\pi_k}_q.w ;\ i \in \{1,2,\ldots,m\};\ q \in \{1,2,\ldots,m\}
\end{equation}

\begin{equation} \label{eq:disttorque}
	s.t.:\ | \sum\ p_i.D * p_i.w\ | \leq maxW \times limit^{CG}_{long} ;\ i \in \{1,2,\ldots,m\}
\end{equation}

Equation \ref{eq:distobj} minimizes the sum of distances of the consolidated in node $\pi_k$ destined to the next node $\pi(k+1)$;

Equation \ref{eq:distcons} states that each consolidated will be assigned to exactly one pallet;

Equation \ref{eq:distpallets} states that each pallet will receive one consolidated;

Equation \ref{eq:distpalletw} calculates the total weight on each pallet (note that it is different from $p_i.W$, the capacity of the pallet); and

Equation \ref{eq:disttorque} guarantees that the torque limit will not be exceeded.

@@

\subsection{Parameters tuning}

A relevant problem with meta-heuristics is the parameter's adjustment to extract the best possible efficiency in the optimization. The bulk of the tools to fine-tune these parameters utilize a statistical backdrop that enables them to make accurate predictions regarding the differences in candidate configurations' performance. Inadequacies in the design of the statistical experiment may therefore lead to erroneous results from the statistical tests and, subsequently, cause the approach to produce inaccurate comparisons of candidate configurations. That is why all parameters were set using the $iRace$ package \cite{LopezIbanezManuel2016}. Supplying $iRace$ with a range for $volThreshold$ as $[0.80,\ 0.99]$, {\it iRace} yielded 0.92, by training on the uneven instances numbers. The values tested for 20\%, 50\%, and 100\% volume surpluses were very close, considering the confidence level offered by {\it iRace}.

For the {\it torque surplus - ts}, we input {\it iRace} with the range $[1.0,\ 2.0]$ and this tool chose $ts = 1.7$ as a value that brings torque of the $Greedy$ first phase to a feasible region.

\subsection{Multiprocessing}

According to \cite[p.271]{Breshears2009}, a {\it Process} is the operating system’s spawned and controlled entity that encapsulates an executing application.

@@

As in the larger aircraft the number of pallets is bigger than the number of threads available in a common handheld computer, for parallelization, we used the {\it Python Multiprocessing} package, which implements {\it process-based parallelism} or {\it parallel shared memory algorithm}. According to \cite{multiprocessing}, {\it Multiprocessing} is a package that supports spawning processes using an API similar to the {\it Python Threading} package.

@@

\vspace{2.0mm}
\begin{table}[!ht]
\centering
\caption{Average distances minimization}  \label{tab:ground}
%\footnotesize
\scriptsize
\begin{tabular}{c S[table-format=-1.1] S[table-format=-1.1] S[table-format=-1.3]}
\toprule
& {\bf Before} & {\bf After} & {\bf Improvement} \\
{\bf Scenario} & {\bf (m)}    & {\bf (m)}   & {\bf (\%)} \\		
\midrule
$1$ &  32.7 &  28.7 & -7.3 \\ % CBC 32.1 & 31.3 & -2.4 Shims 34.0 & 29.5 & -13.1, 31.5 & 29.9 & -5.1
$2$ & 193.3 & 188.9 & -6.3 \\ % mpShims 212.0 & 188.9 & -10.9
$3$ & 165.1 & 153.3 & -7.1 \\ % 
$4$ & 137.1 & 132.0 & -3.7 \\ % CBC 137.1 & 132.0 & -3.7 mpShim 143.4 & 136.6 & -4.7
$5$ & 126.7 & 122.0 & -3.8 \\ % CBC 124.9 & 116.3 & -6.9 mpShim 126.7 & 122.0 & -3.8 
$6$ & 115.3 & 110.4 & -4.2 \\ % CBC 117.4 & 107.6 & -8.3 mpShim 115.3 & 110.4 & -4.2                                                                
\bottomrule
\end{tabular}
\end{table}

Table \ref{tab:ground} presents the distances minimization of the next node destined pallets to the ramp door. Columns {\bf Before} and {\bf After} refer to the application of the current method. In average, the distances from the pallets and the last ramp door position was diminished by 5\% along a tour.

@@

(4) The distances to move pallets on unloading in the next node could be minimized to benefit ground handling costs.
This hypothesis was confirmed by the results on Table \ref{tab:ground}.

@@

Other important contributions are that we verified four hypotheses: Computer parallelism improved {\it Shims} performance; the intermediate integer programming procedure added to {\it Shims} algorithm enhanced it's results; a procedure for 3-D packing was turned possible for operational use due to a process-based parallel computing heuristic, and the integer programming procedure to minimize pallets' travel in the cargo bay was successful.
